SIMD\slash SIMT-vectorized Thermo-chemical Source Term Evaluation

### 2018-02-01 derivations.tex
update

\subsubsection{Temperature source term derivatives}
Starting from~\cref{e:dTdotdT_nojac},~\cref{e:dnkdotdT_compact} is substituted in to yield:

>>>>

\subsubsection{Temperature source term derivatives}
Similarly to~\cref{s:dtdotdt_final},~\cref{e:dnkdotdE_compact} is substituted into~\cref{e:dTdotdE_nojac} to yield:
\loadeq{dTdotdE}
